---
title: "Data Science - Homework #6"
author: "Jon Brock - JPB2210"
output: 
    github_document:
        toc: TRUE
        toc_depth: 2
---

```{r load packages, message = FALSE}
library(tidyverse)
```

***

## Problem #1
###### (*45 points*)
##### *Working with linear models*  

I reviewed each vector to determine what vector type each one should be when imported. There is a majority of integer values, so the `.default` value for non-specified vectors applies as such. I specified `babysex`, `frace`, `malform`, and `mrace` as `<fct>` vectors; `gaweeks`, `ppbmi`, and `smoken` are specified as `<dbl>` vectors. I will further tidy--relevel and relabel--my specified `<fct>` vectors in subsequent code.  

```{r load and tidy data}
bw_df <- read_csv("./data/birthweight.csv",
                  col_names = TRUE,
                  col_types = cols(
                      .default = col_integer(),
                      babysex = col_factor(),
                      frace = col_factor(),
                      gaweeks = col_double(),
                      malform = col_factor(),
                      mrace = col_factor(),
                      ppbmi = col_double(),
                      smoken = col_double()
                      )
                  )

print(bw_df)
```


It is rather tedious to check for `NA` values within individual vectors one at a time. So, instead, I decided to check all vectors at once by using a "soft-deprecated" `dplyr` function (`funs()`) to summarize all of the `NA` observations within each vector in my data frame. The output shows that we have `0` observations of `NA` in all of our vectors. We're good to go!  

```{r checking all columns for na values, warning = FALSE}
bw_df %>% 
    select(everything()) %>% 
    summarize_all(funs(sum(is.na(.))))
```

```{r eval = FALSE}
bw_df %>% 
    mutate(
        babysex = 
    )

```

***  

## Problem #2
###### (*35 points*)
##### *Bootstrapping*  

```{r pre-specified data import code, message = FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

***  

## Return of the Bonus Content  
